### 2022-07-24 paper/akweury/document.tex
fix a bug

\subsection{VIL Net}
Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net). 
The structure is shown in Figure \ref{fig:albedo-gated-archi}. As mentioned in the name, the network utilizes vertex map, light map and image map to accomplish the normal inference task.

The network can be consider in two parts. The first part extracts the feature map encoders. It deals with two kinds of input, the vertex map $ X_1 \in \mathbb{R}^{w\times h\times3}$ and the concatenation of light and image map $ X_2 \in \mathbb{R}^{w\times h\times4} $. The network extracts the geometry features $ X_v $ from vertex map $ X_1 $ (represented as a regression function v)
\[ v: X_1 \rightarrow X_v \]
meanwhile, the network extracts the photometric features $ X_l $ from image and the light map $ X_2 $ (represented as a regression function $ l $)
\[ l: X_2 \rightarrow X_l \]
where the two encoders have the same network architecture based on GCNN model.The second part is basically identify to the original GCNN architecture, but before the start of upsampling part, 2 extra layers are added. First, a concatenate layer is added to fuse the vertex feature and the image and light map feature getting from encoder. 
Second, a fused feature map is predicted from all the feature maps base on a single gated convolution layer. (represented as a regression function $ m $)
\[ m: [X_v X_l] \rightarrow X_f \]
Then the network interpolates the feature maps $ X_f $ using 3 times upsamling with gated convolution layers. Meanwhile, the skip connections from UNet have been kept. Thus the feature maps $ X_{df_1, df_2, ...} $ of each down-sampling time in the regression model $ v $ are considered in the upsamling part.
\[ n: X_f, X_{df_1, df_2, ...} \rightarrow N \]

>>>>

The normal inference task estimate the surface normal of a 3D object. There are two main approach to solve the task. Geometry based approach estimate the surface normal of an object based on the geometry principle. Point cloud is a common surface geometry information which samples the surface point position in 3D space. Another approach is photometric stereo based approach, which utilizes a set of images under different illumination conditions. In this chapter, geometry and photometric stereo based approach are introduced separately, then a deep learning based approach using geometry information is proposed. In the end, as the main work of the thesis, another deep learning method is proposed based on both geometry and photometric stereo information.

\section{Geometry based normal estimation}

\subsection{Approach}
The geometry based normal estimation uses point cloud of the object surface as input.
Given a structured point cloud $ V^{W\times H\times 3} $ to estimate the normal map  $ N^{W\times H \times 3} $, where each normal  $ \textbf{n}^{3\times 1} $ at point $ \textbf{v}^{3\times 1} \in N $ is a unit vector with its direction point outward of the surface and perpendicular to the tangent plane of the surface at point $ \textbf{p}^{3\times 1} $.

The idea behind the neighbor based method is to fit a plane $ \Pi $ using the $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of the point $ \textbf{p} $, calculate the normal  $ \tilde{\textbf{n}} $ of the plane.

It is under the assumption that the point and its neighbors are located in the same plane. This is usually not hold for the most of the surface, but if $ k $ in a suitable scale and point cloud is dense enough, it is enough to get an accurate and sharp result. As shown in Figure \ref{fig:svd-normal}.

Specifically, it is not necessary to find the exact plane equation to solve the normal. Instead, the normal can be derived based on an equation system. 
The normal $ \tilde{\textbf{n}} $ of plane $ \Pi $ is perpendicular to all the vector on the plane $ \Pi $, we can construct $ k $ vectors on plane $ \Pi $ use  $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of point $ \textbf{p} $. For the simplicity, we can choose $ \textbf{p}_1 $ as the base point, then $ k-1 $ vectors can be construct as follows
\begin{equation}
	\begin{array}{rr}
		\displaystyle \textbf{v}_i = \textbf{p}_1 - \textbf{p}_i & \text{for}\ i= 2,...,k \\
	\end{array}
\end{equation}
and each of them satisfied $ \textbf{v}_i \cdot \tilde{\textbf{n}} = 0$. Then, the equation system can be constructed as 
\begin{equation}{\label{eq:normal-overdetermined-equation}}
	A \cdot \textbf{n} = 0
\end{equation}
where $ A \in \mathbb{R}^{(k-1)\times 3} $ is the vector matrix vertically stacked by $ \textbf{v}_1, ..., \textbf{v}_{k-1} $.
In order to avoid trivial solution, one more constraint should be added
\[ \|  \bn_{3 \times 1} \|_2^2 = 1  \]
which also let the normal to be a unit vector.

To calculate a valid normal, at least 3 points are required to construct, i.e. $ k>=3 $. For the sake of robust, more points can be used to reduce the measuring error. For the case $ k>3 $, since the surface vectors are actually not in the same plane, the equation system is likely over-determined . Then the equation system mentioned above can be converted to follow optimization problem
\begin{equation}
	\begin{array}{rrclcl}
		\displaystyle \min & \multicolumn{3}{l}{\| A  \bn \|^2} \\
		\\
		\textrm{s.t.} & \| \bn \|^2 & = & 1 
	\end{array}
\end{equation}
which can be solved by singular value decomposition(SVD). Let the decomposition of 
\[ A=U\Sigma V^T \]
The solution i.e. normal is the last column of $ V $.

At last, all the normals should point ot view point $ \textbf{s} $, thus the direction of a normal should be inverted if 
\begin{equation}\label{eq:normal-invertion}
	\textbf{n} \cdot (\textbf{p}  - \textbf{s}) > 0
\end{equation}

Repeat the procedure for all the points in the point cloud to get the entire normal map.

\subsection{Evaluation}
The neighbor based method can predict the normal map in a good way when the given point cloud is dense, as shown in Figure \ref{fig:svd-normal}. It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.

However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges. This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different. 
\begin{figure}[th]
	\centering
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}

	\label{fig:svd-normal}
	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
\end{figure}
The neighbor based method is depended on a well-chosen parameter $ k $. Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values. When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever. For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon. Compare to the first case, the outline edge error goes better. Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers. However, for the area of horn outline, hindleg outline, the error goes worse. In this case, most of the neighbors of these points are outliers and thus failed this approach.  $ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
	\label{fig:svd-k-eval}
	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
\end{figure}

The performance of neighbor based method is good enough for a well chosen $ k $, and it can be further improved by simply use different $ k $ for different area prediction. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor selection and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\label{fig:svd-noise}
	\caption{Evaluation of neighbor based method on a noised dragon model}
\end{figure}

% ---------------------- gated convolution neural network ------------------------
\section{Gated Convolution neural network for surface normal estimation}
\label{gcnn}

Recently, deep learning based method achieved a great succeed for image processing. ( \cite{yolov3}, \cite{efficientDet}) These network architectures use a batch of RGB / Grayscale images as input and are employed for classification problems. Usually, the images are convoluted with a convolution layer and downsampling with pooling layers. The outputs of the network consist of a single value to represent the index of the corresponding class (\cite{efficientDet}) or with a set of values to represent the position of bounding boxes.(\cite{yolov3}). However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input. Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction. In this case, the traditional network architecture is not suitable anymore.

%% upsampling 
It is worth to noticed that, the output of normal inference CNN model is not one or several labels but an entire image or normal map with same size. 
%% talk about image upsampling, unet
Recently,\cite{unet} proposed an architecture called UNet for biomedical image segmentations. The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size. The proposed network can successfully assigned each pixel a class for segmentation tasks. Under this symmetric network, an input image is downsampled 4 times and upsampled 4 times. Output image has exactly the same size as input image. The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.

\begin{figure}[th]
	\centering
	\includegraphics[width=.8\textwidth]{./Figures/u-net-illustration-correct-scale2.pdf}
	\label{fig:u-net}
	\caption{The structure of UNet. \cite{unet}}
\end{figure}

The UNet is based on standard convolution layers to construct the network. This is reasonable for image processing task with full-dense input, since no missing pixels exist. 
However, for the input of noised point cloud, the valid and invalid pixels will be treated equally if we still perform standard convolution layers. Since the aim of the network is not learning the pattern of noise, but the noise with eternally changing patterns will confuse the network, and it fails the normal inference, a mask is required to distinguish two kinds of pixels.

% why we need a mask
\cite{pncnn0} use binary mask to indicate valid pixels, and further use normalized convolution to predict the output. The normalized convolution is shown as follows

\begin{equation}
	\begin{array}{rrclcl}
		O(x,y) = 
		\begin{cases}
			\dfrac{\Sigma_i^k\Sigma_j^k W(i,j) \cdot I(x-i,y-j) \cdot M(x-i,y-j)}{\Sigma_i^k\Sigma_j^k W(i,j) \cdot M(x-i,y-j)}, & \text{if}\ \sum_{i}^k\sum_{j}^k M(i,j)>0 \\
			0, & \text{otherwise}
		\end{cases}
	\end{array}
\end{equation}

where $ k $ is the kernel size, $ (x,y) $ is the position in input, $ (i,j) $ is the displacement in kenel, $ M $ is the corresponding mask. A binary mask uses 1 to indicate valid pixels and 0 otherwise. $ \odot $ denotes element-wise multiplication.

Normalized convolution layer added the weight to the mask. However, a initialization for the mask is still required, and the propagation of the mask remain a tricky task.

\subsection{Gated Convolution}

% introduce gconv
\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}. 
\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.

The structure is shown in Figure \ref{fig:gconvLayer}. Instead of using a mask as input to indicate valid pixels, it employs a standard convolution layers to learn this mask directly from data. The valid pixels are then activated by a Sigmoid function. Then it imply element-wise multiplication with the feature map. Formally, the gated convolution is described as follows, the layer with input size $ (N, C_{in}, H, W) $ and output size $ (N, C_{out}, H_{out}, W_{out}) $:
\begin{equation}\label{gconv}
	o(N_i, C_{o_j}) = \sigma(\sum_{k=0}^{C_{in}-1}w_g(C_{o_j}, k) \star i(N_i,k) + b_g(C_{o_j})) * 
	\phi (\sum_{k=0}^{C_{in}-1}w_f(C_{o_j}, k) \star i(N_i,k) + b_f(C_{o_j}))
\end{equation}
where $ \phi $ is LeakyReLU function, $ \sigma $ is sigmoid function, thus the output values are in range $ [0,1] $, $ \star $ is the valid 2D cross-correlation operator, $ N $ is batch size, $ C $ denotes a number of channels, $ H $ is a height of input planes in pixels, and $ W $ is width in pixels, $ w(C_{o_j},k) $ denotes the weight of $ j $-th output channel corresponding $ k $-th input channel, $ i(N_i, k) $denotes the input of $ i $-th batch corresponding $ k $-th input channel, $ b(C_{o_j}) $ denotes the bias of $ j $-th output channel.

% Gated Convolution Layer
\begin{figure}[th]
	\centering
	\begin{tikzpicture}
		\tikzstyle{rect} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
		\tikzstyle{arrow} = [thick,->,>=stealth]
		\node (output) [rect] {Output};
		\node (oplus) [below of=output, yshift=-.2cm] {$\Huge\oplus $};
		\node (LeakyReLU) [rect,below of=oplus, yshift=-0.4cm] {Feature};
		\node (sigmoid) [rect, below of=oplus, yshift=-0.4cm, xshift=-4cm] {Mask};

		\node (conv1) [rect,below of=sigmoid, yshift=-1cm] {Mask};
		\node (conv2) [rect,below of=LeakyReLU, yshift=-1cm] {Feature};
		\node (input) [below of=oplus] at (0,-7) {\includegraphics[width=.25\textwidth]{./Figures/train-input.png}};

		\draw [arrow] (oplus) -- (output);
		\draw [arrow] (sigmoid) |- (oplus);
		\draw [arrow] (LeakyReLU) -- (oplus);
		\draw [arrow] (conv2) --  node [text width=2.5cm, midway, right=1em]{LeakyReLU} (LeakyReLU);
		\draw [arrow] (conv1) --  node [text width=2.5cm, midway, right=1em]{Sigmoid} (sigmoid);
		\draw [arrow] (input) -|  node [text width=2.5cm, midway, below=1em]{Conv2D} (conv1);
		\draw [arrow] (input) -- node [text width=2.5cm, midway, right=1em]{Conv2D} (conv2);
	\end{tikzpicture}
	\caption{Gated Convolution Layer, where $ \oplus $ denotes element-wise multiplication.}
	\label{fig:gconvLayer}
\end{figure}

%\section{Canny Edge Detection for Detail Enhancement}
%The inaccuracy part is usually concentrate in the coarse surface or drastic changed surface parts of the object. The corresponding part can be extracted separately via edge detector algorithms, like Canny Edge detector. Feed the edges to a special net for normal prediction might improve the accuracy further.

\subsection{Architecture}
\label{sec:architecture}
Based on the implementation mentioned above, the architecture roughly follows on UNet proposed by \cite{unet}, as shown in Figure \ref{fig:gcnn-archi}.

Instead of using pooling layers for down/up samplings, gated convolution layer with stride $ (1,1) $ is used. The gated convolution using Sigmoid function for gating layer and LeakyReLU function for feature layer. All the layers are gated convolution layer with the exception of last two layers, which instead uses standard convolution layer to scale the output in range $\left[-1, 1\right]$. Other than the last two layers which use $ 1\times 1 $ kernels, all the gated convolution layer use $ 3\times 3 $ kernels with $ 1\times1 $ padding.

The input is 3D vertex with size $ 512\times512\times3 $, and output is $ 512\times512\times3 $ normal map, which has the same resolution. There are 3 times downsamplings, each scale with 3 gated convolution layers, the third layer has stride 2. The upsampling part interpolate the feature maps 3 times with 1 gated convolution layer in each scale.

It keeps the skip connection in UNet to remain the fine detail features.

% GCNN Architecture
\begin{figure}[!h]
	\centering
	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
	\begin{tikzpicture}
		%% -------------------------------------- parameters ------------------------------------------------
		\pgfmathsetmacro{\vdist}{0.4}

		\pgfmathsetmacro{\boxsizea}{3}	%% width 512
		\pgfmathsetmacro{\boxsizeb}{1.5}	%% width 256
		\pgfmathsetmacro{\boxsizec}{1}	%% width 128
		\pgfmathsetmacro{\boxsized}{0.7}	%% width 64

		\pgfmathsetmacro{\boxwidthd}{0.1}	%% width 1
		\pgfmathsetmacro{\boxwidtha}{0.2}	%% width 3
		\pgfmathsetmacro{\boxwidthb}{\boxwidtha*1.3}	%% width 32
		\pgfmathsetmacro{\boxwidthc}{\boxwidtha*3}		%% width 64

		\pgfmathsetmacro{\convwshift}{9}
		\pgfmathsetmacro{\preprocessingshift}{4}
		\pgfmathsetmacro{\labelshift}{1.5}
		\pgfmathsetmacro{\gconvwshift}{0}

		\pgfmathsetmacro{\secrowshift}{-6}

		\pgfmathsetmacro{\convrowstart}{4}
		\pgfmathsetmacro{\secondrowstart}{4}

		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
		\definecolor{gconvcolor}{rgb}{0.5,0.7,0.7}
		\definecolor{convcolor}{rgb}{0.5,0.7,0.3}
		\definecolor{gconvdilatedcolor}{rgb}{0.6,0,0.3}

		%% ---------------------------------- preprocessing --------------------------------------------
		%%  img_in 1x512x512
		\pgfmathsetmacro{\disttimes}{3.5}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {3D Vertex};

		\draw [-stealth](1.45,\yschift-1.8) -- (1.45,\yschift-2.6);

		\draw [-stealth]  (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);

		\pgfmathsetmacro{\disttimes}{10}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-depth-noise}};
		\node[text width=3.5cm] at (\vdist*\disttimes+1,\yschift-1.5) {Add Noise};

		\draw [-stealth] (\vdist*\disttimes+1.6,\yschift) -- (\vdist*\disttimes+1.1,\yschift);

		\pgfmathsetmacro{\disttimes}{16.5}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-depth.png}};
		\node[text width=2cm] at (\vdist*\disttimes+0.2,\yschift-1.5) {Depth Map};

		%% ----------------------------------- output normal map -------------------------------------
		\pgfmathsetmacro{\disttimes}{25}
		\pgfmathsetmacro{\yschift}{\preprocessingshift}
		\node[inner sep=0pt] (depthmap) at (\vdist*\disttimes,\yschift)
		{\includegraphics[width=.15\textwidth]{./Figures/train-normal-gt.png}};
		\node[text width=2.5cm] at (\vdist*\disttimes,\yschift-1.5) {Normal Map};

		\draw [-stealth] (\vdist*\disttimes+0.2,\yschift-2.7) -- (\vdist*\disttimes+0.2,\yschift-1.8);

		%% ------------------------------------------- vertex input ----------------------------------------------
		%% 	d_in							3x512x512
		%%	dconv1: 	d_in-->x1 			32x512x512
		\pgfmathsetmacro{\disttimes}{1}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%%	dconv2:		x1-->x1				32x512x512
		\pgfmathsetmacro{\disttimes}{2}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%%	dconv3:		x1-->x1				32x512x512
		\pgfmathsetmacro{\disttimes}{3}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.2,\yschift-3.2) -- (\vdist*\disttimes-0.2,\yschift-4);
		\draw (\vdist*\disttimes-0.2,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-4);
		\draw [-stealth] (\vdist*\disttimes+6.5,\yschift-4) -- (\vdist*\disttimes+6.5,\yschift-3.2);

		%% downsample 1
		%%	dconv4:		x1-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{4}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x2-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{5}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x2-->x2				32x256x256
		\pgfmathsetmacro{\disttimes}{6}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizeb}	%% size 256
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.5}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.1,\yschift-1.6) -- (\vdist*\disttimes-0.1,\yschift-2.7);
		\draw (\vdist*\disttimes-0.1,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-2.7);
		\draw [-stealth] (\vdist*\disttimes+4.2,\yschift-2.7) -- (\vdist*\disttimes+4.2,\yschift-1.7);

		%% downsample 2
		%%	dconv4:		x2-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{7}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x3-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{8}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x3-->x3				32x128x128
		\pgfmathsetmacro{\disttimes}{9}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizec}	%% size 128
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-0.8}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\draw (\vdist*\disttimes-0.1,\yschift-1.2) -- (\vdist*\disttimes-0.1,\yschift-1.8);
		\draw (\vdist*\disttimes-0.1,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.8);
		\draw [-stealth] (\vdist*\disttimes+1.8,\yschift-1.8) -- (\vdist*\disttimes+1.8,\yschift-1.2);

		%% downsample 3
		%%	dconv4:		x3-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{10}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv2:		x4-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{11}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%%	dconv3:		x4-->x4				32x64x64
		\pgfmathsetmacro{\disttimes}{12}
		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=gconvcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		%		%% dilated
		%		%%	dilated1:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{13}
		%		\pgfmathsetmacro{\boxsize}{\boxsized}	%% size 64
		%		\pgfmathsetmacro{\boxwidth}{\boxwidthb}	%% width 32
		%		\pgfmathsetmacro{\yschift}{\gconvwshift-1}	%% width 32
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		%		\draw[black, fill=gconvdilatedcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;
		%		%%	dilated2:	x4-->x4				32x64x64
		%		\pgfmathsetmacro{\disttimes}{14}
